Identifying Factors That Affect Political Freedom Within the OECD

### 2020-11-25 paper/paper.Rmd
added date

author: 
  - name          : "Joe Despres"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
  - name          : "Sabrina Ball"
    affiliation   : "1"
  - name          : "Jacob Haywood"
    affiliation   : "1"
  - name          : "Joe Sigler"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Michigan State University"

date: 
  - "Last compiled `r format(Sys.time(), '%H:%M')`"

keywords          : "keywords"
wordcount         : "X"

>>>>

author: 
  - name          : "Joe Despres"
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
  - name          : "Sabrina Ball"
    affiliation   : ""
  - name          : "Jacob Haywood"
    affiliation   : ""
  - name          : "Joe Sigler"
    affiliation   : ""

affiliation:
  - id            : ""
    institution   : "Michigan State University  \n  November 30, 2020"

keywords          : "keyword"
wordcount         : "X"

### 2020-11-25 paper/paper.tex
added date

  pdfauthor={Joe Despres1, Sabrina Ball1, Jacob Haywood1, \& Joe Sigler1},

@@

  pdfkeywords={keywords},

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Political Freedom Within the OECD}
\keywords{keywords\newline\indent Word count: X}
\usepackage{lineno}

@@

\title{Identifying Factors That Affect Political Freedom Within the OECD}
\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
\date{Last compiled 21:15}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Michigan State University}

>>>>

  pdfauthor={Joe Despres, Sabrina Ball, Jacob Haywood, \& Joe Sigler},

@@

  pdfkeywords={keyword},

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Political Freedom Within the OECD}
\keywords{keyword\newline\indent Word count: X}
\usepackage{lineno}

@@

\title{Identifying Factors That Affect Political Freedom Within the OECD}
\author{Joe Despres\textsuperscript{}, Sabrina Ball\textsuperscript{}, Jacob Haywood\textsuperscript{}, \& Joe Sigler\textsuperscript{}}
\date{}

\affiliation{\vspace{0.5cm}\textsuperscript{} Michigan State University\\
November 30, 2020}
